\cvsection{Experience}
\begin{cventries}
  \cventry
    {Senior Full Stack Developer \newline\vspace{-4pt} Full Stack Developer}
    {McKinney}
    {Durham, NC}
    { May 2025 - Present \newline\vspace{-4pt} October 2022 - April 2025}
    {
      \begin{cvitems}
      \item Led design, development, and scaling of multiple production-grade ML/AI applications, including BrandAI, Creative Analysis Tool, Keyword Labeling \& Categorization App and AudiencePro \& MSAI feature integrations.
        \item Built and maintained backend systems, delivered low-latency inference services and developed robust API architectures using Python, FastAPI, Cloud Run, ECS/Fargate, OpenSearch, Postgres (pgvector), ChromaDB, and MongoDB.
        \item Developed RAG and LLM-driven workflows, including embedding pipelines, vector store implementations, multi-step agent systems (LangChain, LangGraph), and secure inference services using AWS Bedrock, Hugging Face and Vertex AI.
        \item Designed, trained, and deployed LoRA fine-tuned models (SDXL, Flux) using Vertex AI Pipelines, creating repeatable and scalable MLOps workflows with automated evaluation, model versioning, and MLflow tracking.
        \item Architected cloud infrastructure and implemented consistent, secure, cross-team cloud patterns using GCP (Cloud Run, Cloud Build, Composer, Vertex AI, IAM, Cloud Storage, Artifact Registry) and AWS (ECR, ECS/Fargate, EC2, VPC, IAM, Secrets Manager).
      \end{cvitems}
      \vspace{6pt}
    }
  \cventry
    {Associate Software Engineer}
    {Travelers}
    {Raleigh, NC}
    {June 2021 - October 2022}
    {
      \begin{cvitems}
        \item {Developed and maintained the  Bond Claim Management System and Letter Genie as a part of the Bond Claim and Specialty Insurance division.}
        \item {Development stack included VB.NET, C\#, .NET, Javascript, Microsoft SQL Server, MongoDB, AWS and Git.}
      \end{cvitems}
      \vspace{6pt}
    }
  \cventry
    {Software Developer I}
    {Farragut Systems}
    {Durham, NC}
    {Nov. 2018 - June 2021}
    {
      \begin{cvitems}
        \item {Maintained legacy desktop applications and built web applications from the ground up.}
        \item {Converted Matlab code to Azure Web App, refactored PA Compensation Rating Bureau financial reporting application with data migration, and optimized batch processing.}
        \item {Development stack included C\#, .NET, Oracle SQL, Microsoft SQL Server, Docker, Azure, Git and Subversion}
      \end{cvitems}
      \vspace{6pt}
    }
  \cventry
    {Adjunct Professor, Instructor \& Teaching Assistant}
    {University of Delaware}
    {Newark, DE}
    {Aug. 2013 - July 2018}
    {
      \begin{cvitems}
        \item {Math 242: Analytic Geometry and Calculus B. Topics included exponential and logarithmic functions, sequences, series, integration techniques, parametric curves and polar coordinates.}
        \item {Math 241: Analytic Geometry and Calculus A. Topics included functions, limits, differentiation and integration.}
        \item {Math 230: Finite Mathematics with Applications. Topics included set theory, probability, optimization, linear programming and introductory matrix methods.}
        \item {Math 210: Discrete Mathematics I. Topics included set theory, logic, induction, counting, introductory graph theory and power series.}
      \end{cvitems}
      \vspace{6pt}
    }
  \cventry
    {Research Assistant}
    {University of Delaware}
    {Newark, DE}
    {Aug. 2013 - May 2018}
    {
      \begin{cvitems}
        \item {Applied spectral graph theory to derive structural and combinatorial results from adjacency matrix eigenvalues.}
        \item{Developed Python tools to identify subgraphs with specific structural properties and published findings.}
      \end{cvitems}
      \vspace*{6pt}
    }
\end{cventries}
\vspace*{6pt}
